smooth-sea

### 2018-05-20 index.rmd
slider for index map

```{r index.maps, echo=F}
smoothed <- ggplot(sea_f %>% filter(listingQtr == "2018 Q2"), 
                   aes(x = long, y = lat, group = group, fill = bym_Med, label = GISJOIN)) +
  #facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(limits = c(750, 2500), labels = scales::dollar) +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank()) +
  labs(title = "Spatially Smoothed 1B Median Rent",
       fill = "Smoothed")
ggplotly(smoothed, tooltip = c("label", "fill"))
```

>>>>

```{r index.maps, echo=F}

smoothed <- ggplot(sea_f, 
                   aes(x = long, y = lat, group = group, fill = bym_Med, label = GISJOIN, frame = listingQtr)) +
  #facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(limits = c(750, 2500), labels = scales::dollar) +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank()) +
  labs(title = "Spatially Smoothed 1B Median Rent",
       fill = "Smoothed")
ggplotly(smoothed, tooltip = c("label", "fill"))
```
